```{r}
require(tidyverse)
require(data.table)
require(randomForest)
require(mclust)
require(rpart)
require(rpart.plot)
require(foreign)
require(e1071)
```
Selection
#Data Source
#https://www.kaggle.com/datasets/whenamancodes/credit-card-customers-prediction

Pre-processing
```{r}
BankChurners <- read.csv("./Project_Dataset-20250601/Dataset/BankChurners.csv")
new_custom <- read.csv("./Project_Dataset-20250601/Dataset/new_custom.csv")
new_customer <- read.csv("./Project_Dataset-20250601/Dataset/new_customer.csv")
BankChurners
new_custom
new_customer
BankChurnerscheckNA <- is.na(BankChurners)
BankChurnerscheckNA
new_customcheckNA <- is.na(new_custom)
new_customcheckNA
new_customercheckNA <- is.na(new_customer)
new_customercheckNA
```

Excellent: 0-10% utilization
Good: 10-30% utilization
Fair: 30-50% utilization
Poor: 50% or higher utilization
Transformation
```{r}
Transform <- BankChurners
Transform$Util_Rank <- sapply(Transform$Avg_Utilization_Ratio, function(x) {
                              if (x < 0.1) "Excellent" 
                              else if (x < 0.3) "Good" 
                              else if (x < 0.5) "Fair" 
                              else "Poor"
                        })
Transform
```

Descriptive Analysis
Question1 - Basic Aggregration
```{r}
#Summarise the average credit limit by different card type
averageCredit_Limit <- tapply(Transform$Credit_Limit, Transform$Card_Category, mean)
as.data.frame(averageCredit_Limit)
#count the number of different education level
educationCount <- table(Transform$Education_Level)
as.data.frame(educationCount)
#Summaries Average of Open to buy all Income Category
averageOpen_to_buy <- tapply(Transform$Avg_Open_To_Buy, Transform$Income_Category, mean)
as.data.frame(averageOpen_to_buy)
```

Question2 - Basic statics (Bar)
```{r}

```

Question3 - Basic statics (pie)
```{r}

```

Question4 - Relation(scatter)
```{r}

```

https://www.digitalocean.com/community/tutorials/normalize-data-in-r
https://stats.stackexchange.com/questions/298507/mclust-model-names-corresponding-to-common-models-i-e-those-used-for-lpa-lc
Modelname EEE = Equal variances and equal covariances
if you want to make the clustering like a matrix, try to use modelname EEE
Question5 - Clustering
```{r}

```

Question6 - pattern finding(CART tree)
```{r}

rpart.plot(Tree)
```

Question7 - classification(Naive Bias)
```{r}
#NB Classification


#new customers


#make an enquiry
predict()
```

Question8 - Prediction/simulation (random Forest)
```{r}
#model building


#model testing

#new customer


#choose one row data for testing
predict()
```

Evualtion
#Write you finding in Report, Thanks!
