```{r}
require(tidyverse)
require(data.table)
require(randomForest)
require(mclust)
require(rpart)
require(rpart.plot)
require(foreign)
require(e1071)
```
Selection
#Data Source
#https://www.kaggle.com/datasets/whenamancodes/credit-card-customers-prediction

Pre-processing
```{r}
BankChurners <- read.csv("./Project_Dataset-20250601/Dataset/BankChurners.csv")

BankChurners

BankChurnerscheckNA <- is.na(BankChurners)
BankChurnerscheckNA

```

Excellent: 0-10% utilization
Good: 10-30% utilization
Fair: 30-50% utilization
Poor: 50% or higher utilization
Transformation
```{r}
Transform <- BankChurners
Transform$Util_Rank <- sapply(Transform$Avg_Utilization_Ratio, function(x) {
                              if (x < 0.1) "Excellent" 
                              else if (x < 0.3) "Good" 
                              else if (x < 0.5) "Fair" 
                              else "Poor"
                        })
Transform
```

Descriptive Analysis
Question1 - Basic Aggregration
```{r}
#Summarise the average credit limit by different card type
avgCreditLimit <- tapply(Transform$Credit_Limit, Transform$Card_Category, mean)
as.data.frame(avgCreditLimit)
#count the number of different education level
educationCount <- table(Transform$Education_Level)
as.data.frame(educationCount)
#Summaries Average of Open to buy all Income Category
avgOpentobuy <- tapply(Transform$Avg_Open_To_Buy, Transform$Income_Category, mean)
as.data.frame(avgOpentobuy)
```

Question2 - Basic statics (Bar)
```{r}
avgSorted <- sort(avgOpentobuy, decreasing = TRUE)
barplot(avgSorted, 
        main = "Average Open to Buy by Income Category",
        xlab = "Income Category", 
        ylab = "Average Open To Buy",
        cex.names = 0.7)
```

Question3 - Basic statics (pie)
```{r}
educationCount <- sort(educationCount,decreasing = TRUE)
pie(educationCount,
    labels = names(educationCount))
```

Question4 - Relation(scatter)
```{r}
#fit <- Mclust(Transform[, c("Total_Trans_Amt", "Total_Trans_Ct")])
plot(Transform$Total_Trans_Amt, Transform$Total_Trans_Ct,
     xlab = "Transform$Total_Trans_Amt",
     ylab = "Transform$Total_Trans_Ct")

abline(lm(Transform$Total_Trans_Ct ~ Transform$Total_Trans_Amt), col = "red")

model <- lm(Total_Trans_Ct ~ Total_Trans_Amt, data = Transform)
rSquared <- summary(model)$r.squared

text(x = max(Transform$Total_Trans_Amt) * 0.62, 
     y = max(Transform$Total_Trans_Ct) * 0.61, 
     labels = bquote(R^2 == .(round(rSquared, 2)))
     )
```

https://www.digitalocean.com/community/tutorials/normalize-data-in-r
https://stats.stackexchange.com/questions/298507/mclust-model-names-corresponding-to-common-models-i-e-those-used-for-lpa-lc
Modelname EEE = Equal variances and equal covariances
if you want to make the clustering like a matrix, try to use modelname EEE
Question5 - Clustering
```{r}
set.seed(114515)
fit <- Mclust(Transform[,c("Total_Trans_Ct","Customer_Age")],G = 4,modelNames = "EEE")
plot(fit, what = "classification",
     xlab = 'Transform.Total_Trans_Ct',
     ylab = 'Transform.Customer_Age')
```

Question6 - pattern finding(CART tree)
```{r}
size <- nrow(Transform)
training <- sample(seq(size),size*0.7,replace = F)
train <- Transform[training,]
test <- Transform[-training,]
set.seed(114514)
Tree <- rpart(Util_Rank~Total_Revolving_Bal+Income_Category,data = train)
rpart.plot(Tree)
```

Question7 - classification(Naive Bias)
```{r}
#NB Classification
model <- naiveBayes(Util_Rank ~ Customer_Age
                    +Gender
                    +Dependent_count
                    +Education_Level
                    +Marital_Status
                    +Income_Category
                    +Months_on_book
                    +Total_Relationship_Count, data = Transform)

#new customers
new_custom <- read.csv("./Project_Dataset-20250601/Dataset/new_custom.csv")
new_customer <- read.csv("./Project_Dataset-20250601/Dataset/new_customer.csv")
#make an enquiry
predict(model, new_custom)
predict(model, new_customer)

```

Question8 - Prediction/simulation (random Forest)
```{r}
#model building
model <- randomForest(formula=Credit_Limit ~ Customer_Age
                      +Gender
                      +Dependent_count
                      +Education_Level
                      +Marital_Status
                      +Income_Category
                      +Months_on_book
                      +Total_Relationship_Count, data = Transform,ntree=1000)

#model testing
plot(model)
#new customer


#choose one row data for testing
predict(model, new_custom)
predict(model, new_customer)
```

Evualtion
#Write you finding in Report, Thanks!
```{r}

```

